Simulation Study: Informative Covariate (cosine)

### 2018-09-06 datasets/simulations/simulations-informative-cosine.Rmd
Change t-5 effect sizes to match others for base cases

```{r t5-parameters}
es_dist <- rnorm_generator(6)    # functional: dist of alternative test stats
ts_dist <- rt_perturber(5)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)    # functional: dist to calc p-values
seed <- 815
```

>>>>

```{r t5-parameters}
es_dist <- rnorm_generator(3)    # functional: dist of alternative test stats
ts_dist <- rt_perturber(5)  # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)    # functional: dist to calc p-values
seed <- 815
```
